MSAD_PCA_Walkthrough

### 2017-01-13 Simulation_Vignette.Rmd
Finished vignette edits

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package. CURRENT ISSUES: remove only alarmed observations, not flagged observations. Set up a replicate structure to repeat this proccess 1000 times.
```{r msad-pca}
Sys.time()
results_ls <- mspMonitor(data = faults_ls$normal[,2:4],
                         labelVector = faults_ls$normal[,1],
                         trainObs = 2880,
                         updateFreq = 1440)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).

>>>>

## Multi-State AD-PCA Implementation
We now throw all this data we've just generated into our package. CURRENT ISSUES: remove only alarmed observations, not flagged observations. Set up a replicate structure to repeat this proccess 1000 times.
```{r msad-pca}
Sys.time()
results_ls <- mvMonitoring::mspMonitor(data = faults_ls$normal[,2:4],
                         labelVector = faults_ls$normal[,1],
                         trainObs = 2880,
                         updateFreq = 1440)
Sys.time() # 14 seconds for 720 train, 360 update; 5 seconds for 1440, 720;
# 1 second for 2880 train (two days), and 1440 update (one day).
